Non-kissing complexes and tau-tilting for gentle algebras

### 2018-07-03 draft/accordionComplexSurfaces.tex
demo nKC incomplète

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{enumerate}[(i)]
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides
\begin{alignat*}{2}
& \Enrs{\alpha} = [v(\alpha), s(\alpha)] \qquad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \qquad & \text{(colored green)} \\
\text{and} \qquad & \Ers{\alpha} = [v\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [v\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
\end{alignat*}
placed as follows:

@@

\begin{definition}
For any arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$,
let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, this common substring~$\sigma$ is strict, so~$\mu_\star$ and~$\nu_\star$ split at one endpoint of~$\sigma$.
The \defn{countercurrent order at~$\alpha$} is defined by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
\end{definition}
\pierreguy{Add a picture here?}

\begin{remark}
\label{rema:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
\pierreguy{Should we prove this?}
\pierreguy{Add picture.}
\end{remark}

For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, we denote by~$F_\alpha$ the set of walks of~$F$ marked at an occurence of~$\alpha^\pm$.

\begin{lemma}
\label{lemm:countercurrentOrderIsTotal}
For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the countercurrent order~$\prec_\alpha$ defines a total order on~$F_{\alpha}$.
\end{lemma}
\begin{proof}
 The proof of \cite[Lemma 2.21]{PaluPilaudPlamondon} applies here.
\end{proof}

\begin{lemma}
\label{lemm:facesHaveMaximalElement}
For any face~$F$ of~$\NKC$ and any arrow~$\alpha\in Q_1\blossom$, the set~$F_\alpha$ admits a maximal element for the countercurrent order~$\prec_\alpha$.
\end{lemma}
\begin{proof}
 We provide two proofs of the lemma.  One is combinatorial and applies to~$\NKC$, and the other is geometric and applies to~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, using the isomorphism of Theorem \ref{thm:complexesCoincide} and Remark \ref{rema:countercurrentOrderOnSurface}.

 {\it Geometric proof.} Let~$F$ be a face of the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$.
\end{proof}

>>>>

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a locally gentle bound quiver~$\bar Q = (Q,I)$ is the surface obtained from the blossoming quiver~$\bar Q\blossom$ as follows:
\begin{enumerate}[(i)]
\item for each arrow~$\alpha \in Q_1\blossom$, consider a lozange~$L(\alpha)$ with four (oriented) sides
\begin{alignat*}{2}
& \Enrs{\alpha} = [v(\alpha), s(\alpha)] \qquad & \Enrt{\alpha} = [v(\alpha), t(\alpha)] \qquad & \text{(colored green)} \\
\text{and} \qquad & \Ers{\alpha} = [v\dual(\alpha), s(\alpha)] \qquad & \Ert{\alpha} = [v\dual(\alpha), t(\alpha)] \qquad & \text{(colored red)}
\end{alignat*}
placed as foll:qows:

@@

\begin{definition}
Consider an arrow~$\alpha \in Q\blossom_1$ and any two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at an occurrence of~$\alpha^\pm$.
Let~$\sigma$ denote their maximal common substring containing that occurrence of~$\alpha$.
Since~$\mu_\star \ne \nu_\star$, their common substring~$\sigma$ is strict, so that~$\mu_\star$ and~$\nu_\star$ split at least at one endpoint of~$\sigma$.
We define the \defn{countercurrent order at~$\alpha$} by~$\mu_\star \prec_\alpha \nu_\star$ when~$\mu_\star$ enters and/or exits~$\sigma$ in the direction pointed by~$\alpha$, while~$\nu_\star$ enters and/or exits~$\sigma$ in the direction opposite to~$\alpha$.
\end{definition}
\pierreguy{I need to modify these two definitions.}

### 2018-07-03 firstPaper/nonKissingComplex.tex
demo nKC incomplète

Consider now an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$.
Let~$F_\alpha$ be the set of walks of~$F$ containing~$\alpha$, marked at an occurrence of~$\alpha$.
Note that~$F_\alpha \ne \varnothing$ since it contains at least the straight walk passing through~$\alpha$, marked at~$\alpha$.
Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
On the other hand, \textcolor{red}{ the proposition below shows that} we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
\begin{proposition}\label{prop: nk facets are finite}
\textcolor{red}{The facets of the non-kissing complex have finite cardinality.}
\end{proposition}

\begin{proof}\textcolor{red}{
Let~$F$ be a non-kissing facet.
Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
Let~$\sigma$ be the longest common substring of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ while the subword~$\sigma$ of~$\mu$ containing~$\beta_1$ is at the top of~$\mu$.
Hence,~$\mu$ kisses itself, which is absurd.}
\end{proof}

>>>>

Consider now an arrow~$\alpha \in Q\blossom_1$ and a non-kissing face~$F \in \NKC$ containing the straight walk passing through~$\alpha$.
Let~$F_\alpha$ be the set of walks of~$F$ containing~$\alpha$, marked at an occurrence of~$\alpha$.
Note that~$F_\alpha \ne \varnothing$ since it contains at least the straight walk passing through~$\alpha$, marked at~$\alpha$.
Observe that this straight walk is always the minimal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$, since it always agrees with the direction of~$\alpha$.
On the other hand, \textcolor{red}{ the proposition below shows that} we can consider the maximal marked walk of~$F_\alpha$ for the order~$\prec_\alpha$.
Intuitively, it is the most countercurrent walk passing through~$\alpha$ with respect to the direction of~$\alpha$.
\begin{proposition}\label{prop: nk facets are finite}
\textcolor{red}{The faces of the non-kissing complex have finite cardinality.}
\end{proposition}

\begin{proof}\textcolor{red}{
Let~$F$ be a non-kissing face.
Since the quiver~$Q$ has a finite number of arrows, it is enough to prove that each~$F_\alpha$ is finite.
Assume, by means of contradiction, that there is some~$\alpha\in Q_1$ with~$F_\alpha$ infinite.
Call ``junction'' a marked occurrence of an arrow~$\beta$ in some~$\omega_\star, \omega'_\star\in F_\alpha$, such that~$\omega$ and~$\omega'$ coincide from their marked occurrence of~$\alpha$ up to~$\beta$ and differ after~$\beta$.
Since~$F_\alpha$ is infinite, there is an infinite number of junctions.
Since~$Q_1$ is finite, there are two junctions with the same underlying arrow~$\beta$ and such that either~$\alpha$ points towards both junctions or~$\alpha$ points to the direction opposite to both junctions.
This shows that there exist three marked walks~$\nu_\star\prec_\alpha \mu_\star\prec_\alpha \lambda_\star\in F_\alpha$ such that~$\lambda, \mu$ and $\nu$ coincide from their marked occurrence of~$\alpha$ up to some marked occurrence~$\beta_1$ of~$\beta$, after which~$\lambda$ differs from~$\mu$ and~$\nu$ but~$\mu$ and~$\nu$ coincide up to some other occurrence~$\beta_2$ of~$\beta$, and then differ (see Figure~\ref{fig: nk facets are finite}).
Let~$\sigma_1$ and~$\sigma_2$ be the longest common substrings of~$\lambda$ and~$\nu$ containing~$\beta_1$ and~$\beta_2$ respectively.
Note that, since~$\nu$ is finite,~$\sigma_2$ cannot contain~$\beta_1$; in particular,~$\sigma_2$ is contained in~$\mu$.
If~$\sigma$ is on top of~$\nu$, then it is at the bottom of~$\lambda$, and~$\lambda$ kisses~$\nu$, which is absurd.
Otherwise, the subword~$\sigma$ of~$\mu$ containing~$\beta_2$ is at the bottom of~$\mu$ and $\lambda$ constains a substring of the form~$\gamma^{-1}\sigma_1$, where~$\gamma$ is an arrow of~$Q$.
If~$\mu$ entirely contains~$\gamma^{-1}\sigma_1$, then~$\sigma_1$ is at the top of~$\mu$.
Hence,~$\mu$ kisses itself, which is absurd.
Therefore,~$\gamma^{-1}\sigma_1$ is not entirely contained in~$\mu$.}
\end{proof}
